Considering scale in multilayer animal social networks

### 2020-06-17 paper/manuscript.Rmd
rest of methods edits

We generated multilayer networks across a series of spatial distance thresholds
for group assignment. Spatial distance thresholds (5, 25, 50, 75, 100, 250 and
500 m) represented a range of visual (short distance) to auditory (long
distance) sensory modalities of caribou. Multilayer networks consisted of the
social association between `r DT[, uniqueN(get(idcol))]` individuals across
three habitat layers (open, forest and forage) for the entire study period. At
the finest scale, individuals within 5 m of one another were considered in the
same group, whereas at the coarsest scale, individuals within 500 m of one
another were considered in the same group. We calculated graph strength and
multidegree for each habitat layer and spatial distance threshold, and edge
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial distance
threshold.

### Spatial scale
To assess the influence of spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales (100
- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
moving window method using a circular window corresponding to the above scales
[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
for caribou during foraging, while re-sampling at 500 m , 750 m and 1000 m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
multilayer network consisting of the social association between 
`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
forage) for the entire study period. Social associations of individuals were
defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
strength and multidegree for each habitat layer and spatial scale, and edge
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial scale.

### Temporal scale
#### Time windows 
We used a temporal multilayer network to assess the seasonality of caribou
sociality. Multilayer networks consisted of the social association between 
`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36 <!--QW: why 35-36 and not just 35 or 36?-->
days taken from the entire study period. Social associations were defined by
spatiotemporal overlap of individuals within 5 minutes and 50 m. In each time
window, we calculated individual graph strength and multidegree, and across the
series of networks, we calculated edge overlap to determine proportion of total
edges observed in each time window.

>>>>

We generated multilayer networks across a series of spatial distance thresholds 
that relate to behavioural interactions that could occur within those distances
<!-- JWT: or something like that needs to be in the first sentence to relate the spatial distance to social scale upfront -->
for group assignment. Spatial distance thresholds (5, 25, 50, 75, 100, 250 and
500 m) represented a range of visual (short distance) to auditory (long
distance) sensory modalities of caribou. Multilayer networks consisted of the
social association between `r DT[, uniqueN(get(idcol))]` individuals across
three habitat layers (open, forest and forage) for the entire study period. At
the finest scale, individuals within 5 m of one another were considered in the
same group, whereas at the coarsest scale, individuals within 500 m of one
another were considered in the same group. We calculated graph strength and
multidegree for each habitat layer and spatial distance threshold, and edge
<!-- JWT: can we call spatial distance social distance? -->
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial distance
threshold.

### Spatial scale
To assess the influence of spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales (100
- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
moving window method using a circular window corresponding to the above scales
[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
for caribou during foraging, while re-sampling at 500 m , 750 m and 1000 m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
multilayer network consisting of the social associations between 
`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
forage) for the entire study period. Social associations of individuals were
defined by spatiotemporal overlap within 5 minutes and 50 m. We calculated graph
strength and multidegree for each habitat layer and spatial scale, and edge
overlap across the entire series of networks to determine proportion of total
edges observed in each combination of habitat layer and spatial scale.
<!-- JWT: Your graphs present things in the order of Forage, Forest, Open, but in the text you do open, forest, forage. They need to be consistent -->

### Temporal scale
#### Time windows 
We used a temporal multilayer network to assess the seasonality of caribou
sociality. Multilayer networks consisted of the social associations between 
`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36 <!--QW: why 35-36 and not just 35 or 36?-->
days taken from the entire study period. Social associations were defined by
spatiotemporal overlap of individuals within 5 minutes and 50 m. In each time
window, we calculated individual graph strength and multidegree, and across the
series of networks, we calculated edge overlap to determine proportion of total
edges observed in each time window.
